Operational Feature Selection with Gaussian Mixture Models for remote sensing images

### 2016-10-12 paper.tex

\begin{proof}[Proof of proposition~(\ref{eq:update-log})]
    {\footnotesize
    \begin{align*}
        \log &\left(|\boldsymbol{\Sigma}_c^{(k)}|\right) =
        \log \left(\left|
            \bigg[\begin{array}{cc}
                \boldsymbol{\Sigma}_c^{(k-1)} & \mathbf{u}_c      \\
                \mathbf{u}_c^t          & \sigma^{(k)}_c \\
            \end{array}\bigg]
        \right|\right) \\
        =&\log \left(\left|
            \bigg[\begin{array}{cc}
                \boldsymbol{\Sigma}_c^{(k-1)} & \mathbf{0}_{k-1,1}     \\
                \mathbf{u}_c^t          & 1 \\
            \end{array}\bigg]
            \bigg[\begin{array}{cc}
                \mathbf{I}_{k-1} & (\boldsymbol{\Sigma}_c^{(k-1)})^{-1} \mathbf{u}_c      \\
                \mathbf{0}_{k-1,1}^t          & \sigma^{(k)}_c - \mathbf{u}_c^t(\boldsymbol{\Sigma}_c^{(k-1)})^{-1} \mathbf{u}_c\\
            \end{array}\bigg]
        \right|\right) \\
        =&\log \left(\left|
            \bigg[\begin{array}{cc}
                \boldsymbol{\Sigma}_c^{(k-1)} & \mathbf{0}_{k-1,1}     \\
                \mathbf{u}_c^t          & 1 \\
            \end{array}\bigg]
        \right|\right)
        +\log \left(\left|
            \bigg[\begin{array}{cc}
                \mathbf{I}_{k-1} & (\boldsymbol{\Sigma}_c^{(k-1)})^{-1} \mathbf{u}_c      \\
                \mathbf{0}_{k-1,1}^t          & \alpha_c \\
            \end{array}\bigg]
        \right|\right) \\
        =&\log \left( |\boldsymbol{\Sigma}_c^{(k-1)}| |1| \right) + \log \left( |\mathbf{I}_{k-1}| |\alpha_c| \right)\\
        =&\log \left( |\boldsymbol{\Sigma}_c^{(k-1)}| \right) + \log ( \alpha_c )
    \end{align*}
    }
    \noindent where $\mathbf{I}_{k-1}$ is the $(k-1) \times (k-1)$ identity matrix and $\mathbf{0}_{k-1,1}$ is the $(k-1) \times 1$ null vector.

>>>>

\begin{proof}[Proof of proposition~(\ref{eq:update-log})]

    % {\footnotesize
    % \begin{align*}
    %     \log &\left(|\boldsymbol{\Sigma}_c^{(k)}|\right) =
    %     \log \left(\left|
    %         \bigg[\begin{array}{cc}
    %             \boldsymbol{\Sigma}_c^{(k-1)} & \mathbf{u}_c      \\
    %             \mathbf{u}_c^t          & \sigma^{(k)}_c \\
    %         \end{array}\bigg]
    %     \right|\right) \\
    %     =&\log \left(\left|
    %         \bigg[\begin{array}{cc}
    %             \boldsymbol{\Sigma}_c^{(k-1)} & \mathbf{0}_{k-1,1}     \\
    %             \mathbf{u}_c^t          & 1 \\
    %         \end{array}\bigg]
    %         \bigg[\begin{array}{cc}
    %             \mathbf{I}_{k-1} & (\boldsymbol{\Sigma}_c^{(k-1)})^{-1} \mathbf{u}_c      \\
    %             \mathbf{0}_{k-1,1}^t          & \sigma^{(k)}_c - \mathbf{u}_c^t(\boldsymbol{\Sigma}_c^{(k-1)})^{-1} \mathbf{u}_c\\
    %         \end{array}\bigg]
    %     \right|\right) \\
    %     =&\log \left(\left|
    %         \bigg[\begin{array}{cc}
    %             \boldsymbol{\Sigma}_c^{(k-1)} & \mathbf{0}_{k-1,1}     \\
    %             \mathbf{u}_c^t          & 1 \\
    %         \end{array}\bigg]
    %     \right|\right)
    %     +\log \left(\left|
    %         \bigg[\begin{array}{cc}
    %             \mathbf{I}_{k-1} & (\boldsymbol{\Sigma}_c^{(k-1)})^{-1} \mathbf{u}_c      \\
    %             \mathbf{0}_{k-1,1}^t          & \alpha_c \\
    %         \end{array}\bigg]
    %     \right|\right) \\
    %     =&\log \left( |\boldsymbol{\Sigma}_c^{(k-1)}| |1| \right) + \log \left( |\mathbf{I}_{k-1}| |\alpha_c| \right)\\
    %     =&\log \left( |\boldsymbol{\Sigma}_c^{(k-1)}| \right) + \log ( \alpha_c )
    % \end{align*}
    % }
    % \noindent where $\mathbf{I}_{k-1}$ is the $(k-1) \times (k-1)$ identity matrix and $\mathbf{0}_{k-1,1}$ is the $(k-1) \times 1$ null vector.
  From eq.~(\ref{eq:cov}) and standard results for the determinant of block matrix~\cite[Chapter 9]{IMM2012-03274} we have immediatly:
  \begin{align*}
    \log \left(|\boldsymbol{\Sigma}_c^{(k)}|\right)  & = \log\left(|\boldsymbol{\Sigma}_c^{(k-1)}|\right)\log\left(\sigma^{(k)}_c  - \mathbf{u}_c^t (\boldsymbol{\Sigma}_c^{(k-1)})^{-1}  \mathbf{u}_c\right)\\
    &= \log\left(|\boldsymbol{\Sigma}_c^{(k-1)}|\right)\log\left(\alpha_c\right)
  \end{align*}
